% abstract.tex
%
% This file has the abstract for the withesis style documentation
%
% Eric Benedict, Aug 2000
%
% It is provided without warranty on an AS IS basis.

\noindent       % Don't indent this paragraph.
This is not a thesis or dissertation and Master \TeX nician is not a
degree granted at the University of Wisconsin-Madison.

\vspace*{0.5em}
\noindent       % Don't indent this paragraph.
This explains the basics for using \LaTeX\ to typeset a dissertation,
thesis or masters project or preliminary report for the University of 
Wisconsin-Madison. Chapter
1 talks briefly about the thesis formatting at UW-Madison.  Chapter 2 gives
an overview of the ``essentials'' of \LaTeX{} and was written by Jon Warbrick.
Chapter 3 talks about figures and tables and what a {\em float} is.  Chapter 4
briefly introduces the {\sc Bib}\TeX{} program.  And finally, Chapter 5 discusses
some of the details for using the {\tt withesis} style file.  The material in
Chapters 2-4 basically are a review of fundamental \LaTeX{} usage and form
a reasonable basic tutorial.

\vspace*{0.5em}
\noindent       % Don't indent this paragraph.
The style discussed in this manual was originally written by Dave Kraynie and
edited by James Darrell McCauley as the {\tt puthesis} style for Purdue
University's theses.  This style was modified to form the {\tt withesis} style. This
manual is largely based on a similar manual by James Darrell McCauley and Scott Hucker.
Permission to use, copy, modify and distribute this software and its documentation
for any purpose and without fee is here by granted.  This software and its documentation
is provided ``as is'' without any express or implied warranty.
