% usage.tex
%
% This file explains how to use the withesis style
%   it is heavily modelled after a similar chapter by McCauley
%   for the Purdue Thesis style
%
% Eric Benedict, May 2000
%
% It is provided without warranty on an AS IS basis.


\chapter{Using the {\tt withesis} Style}

You can get a copy of the \LaTeX{} style for creating a University
of Wisconsin--Madison thesis or dissertation from:

{\tt http://www.cae.wisc.edu/\verb+~+benedict/LaTeX.html}

After somehow unpacking it, you will have the style files ({\tt withesis.sty}
{\tt withe10.sty}, and {\tt withe12.sty}) as well the files used to create
this document.  The files used for this document can be copied and used as a
template for your own thesis or dissertation.

The final printed form of this document is useful, but the
combination of the source code and final copy form a much more valuable
reference.  Keeping a working copy of the this document can be helpful
when you are later working on your thesis or disseration and want to know
how to do something.  If you find a similar example in this document,
then you can simply look at the corresponding source code and add it to
your document.    Because many parts of this document were written by
different people, the styles and techniques are also different and provide
different ways of achieving the same or similar results.

Because of the typical size of theses, it makes sense to break the document
up into several smaller files.  Usually this is done at the chapter level.
These files can then be {\tt \verb|\include|}d in a {\em root} file.  It is
the {\em root} file that you will run \LaTeX{} on.  For this manual, the
root file is called {\tt main.tex}.

\section{The Root File and the Preamble}
The {\tt \verb|\documentclass|} command is used to tell \LaTeX{} that you will
be using the {\tt withesis} document class and it is the first command in your
root file.  Class options such as {\tt 10pt}, {\tt 12pt}, {\tt msthesis} or
{\tt margincheck} are specified here:

{\tt \verb|\documentclass[12pt,msthesis]{withesis}|}

The class option {\tt msthesis} sets the margins to be appropriate for depositing
with the UW library, namely a 1.25 inch left margin with the remaining margins 1 inch.
The defaults for the title page are also defined for a thesis and for a Master of
Science degree.

The class option {\tt margincheck} will place a small black square at the end of
each line which exceeds the margins.\footnote{In reality, the square is
placed at the end of lines which exceed their {\tt \char92hbox}.  This usually
(but not always) indicates a  margin violation on the right margin.  Left
margin violations aren't indicated and if the margin violation is large enough,
there isn't room for the black box to be visiable.}  This is visible both in the {\tt .dvi} file
as well as in the {\tt .ps} file.

The area immediately following this command is called the {\em preamble} and is
used for things like including different style packages,
defining new macros and declaring the page style.

The style packages can be used to easily change the thesis font.  For example,
this document is set in Times Roman instead of the \LaTeX default of Computer
Modern.  This change was performed by including the {\tt times} package:

{\tt\verb|\usepackage{times}|}\footnote{In this document, the typewriter font
{\tt $\backslash$tt} was redefined to use the Computer Modern font with the command
{\tt $\backslash$renewcommand\{$\backslash$ttdefault\}\{cmtt\}}.  
For more information, see~\cite{goossens}.}

Remember that if you change the fonts from the default Computer Modern to
PostScript ({\em e.g.} Times Roman) then in order to correctly see the
document, you will need to convert the {\tt *.dvi} output into a {\tt *.ps}
file and view the document with a PostScript viewer. This is required since 
most {\tt *.dvi} previewer programs cannot 
display PostScript fonts.  Usually, the previewer will substitute
default fonts so the document may be viewed; however, since the alternate
fonts may not be the same size, the formatting of the document may appear
to be incorrect.

The style package for including Postscript figures, {\tt epsfig}, is included with

{\tt\verb|\usepackage{epsfig}|}

If multiple style packages are required, then they can be combined into one statement
as follows:

{\tt\verb|\usepackage{epsfig,times}|}

Many different style packages are available.  For more information, see~\cite{goossens}.

The page styles are defined using a similar method.
A special style is defined for the {\tt withesis} style:

{\tt\verb|\pagestyle{thesisdraft}|}

This style causes the footer text to become:

{\verb| DRAFT: Do Not Distribute        <time><Date>        <input file name>|}

This appears at the bottom of every page.

In addition to the page style command, the {\tt withesis} has defined several useful
commands which are specified in the preamble.  They include {\tt \verb| \draftmargin|},
{\tt \verb|\draftscreen|}, {\tt \verb|\noappendixtables|}, and
{\tt \verb|\noappendixfigures|}.

The command  {\tt \verb|\draftmargin|} draws a PostScript box with the dimensions of
the margins.  This makes it easy to check that the margins are correct and to see if
any of the text or figures are outside of the required margins.  This box is only visible
in the {\tt .ps} file since it is a PostScript special.


The command  {\tt \verb|\draftscreen|} draws a PostScript screen with the word {\em DRAFT}
in light grey and diagonally across the page.  This screen is only visible
in the {\tt .ps} file since it is a PostScript special.

The commands {\tt \verb|\noappendixtables|} and/or {\tt \verb|\noappendixfigures|} should
be used if the appendix does not have either tables or figures respectively.  These commands
inhibit the Appendix Table or Appendix Figure titles in the List of Tables or List of
Figures.\label{usage:noapp}


If you have specified the {\tt psfig} or {\tt epsfig} document style package, then a useful
command is {\tt \verb|\psdraft|}.  This command will show the bounding box that the figure
would occupy (instead of actually including the figure).  This speeds up the draft copy
printing, reduces toner usage and the drawn box is visible in the {\tt .dvi} file.

The next usual command is {\tt \verb|\begin{document}|}.  The following example is part
of the root file used for this manual.

\begin{quote} \singlespace\footnotesize\tt
\begin{verbatim}
\bibliographystyle{plain}
\include{prelude}        % Title page, abstract, table of contents, etc
\include{intro}          % Chapter 1
\include{essentials}     % Edited ``Essential LaTeX'' by Jon Warbrick
\include{figs}           % Chapter 3 Edited from UW Math Dept's Sample Thesis
\include{bibs}           % Chapter 4 From PU Thesis styles, by J.D. McCauley
\include{usage}          % Chapter 5 Strongly based on similar by J.D. McCauley
\bibliography{refs}      % Make the bibliography
\begin{appendices}       % Start of the Appendix Chapters.  If there is only
                         % one Appendix Chapter, then use \begin{appendix}
\include{code}         % Including computer code listings
\include{bibref}         % a BibTeX reference
\include{math}           % Complex Equations from the UW Math Department
\include{acro}           % A discussion on generating PDF files.
\end{appendices}         % End of the Appendix Chapters.  ibid on \end{appendix}
%\include{vita}          % Optional Vita, use \begin{vita} vita text \end{vita}
\end{document}
\end{verbatim}
\end{quote}

\section{Prelude}
After the {\tt \verb|\begin{document}|} comes the preliminary information found in
theses.  In this manual, the information is kept in the file {\tt prelude.tex} (see
above).  These pages will need to be numbered with roman numerals, so use
\begin{quote}\tt\singlespace\begin{verbatim}
\clearpage\pagenumbering{roman}
\end{verbatim}\end{quote}

Next, comes your thesis or dissertation title, your name, date of graduation, department
and degree.
\begin{quote}\tt\singlespace\begin{verbatim}
\title{How to \LaTeX\ a Thesis}
\author{Eric R. Benedict}
\date{2000}
%   - The default degree is ``Doctor of Philosophy''
%     Degree can be changed using the command \degree{}
%\degree{New Degree}
%   - for a PhD dissertation (default), specify \dissertation
%\dissertation
%   - for a masters project report, specify \project
%\project
%   - for a preliminary report, specify \prelim
%\prelim
%   - for a masters thesis, specify \thesis
%\thesis
%   - The default department is ``Electrical Engineering''
%     The department can be changed using the command \department{}
%\department{New Department}
\end{verbatim}\end{quote}

If you specified the class option {\tt msthesis}, then the degree is changed to
{\em Master \break of Science} and the {\tt \verb|\thesis|} option is specified.  If you
want to have the masters margins with another document, then the {\tt \verb|\degree|}
and {\tt \verb|\dissertation|},  {\tt \verb|\project|}, {\em etc.\/} can be specified
as needed.

Once the
above are all defined, use  {\tt \verb|\maketitle|} to generate the title page.
\begin{quote}\tt\singlespace\begin{verbatim}
\maketitle
\end{verbatim}\end{quote}

If you wish to include a copyright page (see Section~\ref{copyright} for
information on registering the copyright.), then add the command
\begin{quote}\tt\singlespace\begin{verbatim}
\copyrightpage
\end{verbatim}\end{quote}
This will generate the proper copyright page and will use the name and date specified
in {\tt \verb|\author{}|} and {\tt \verb|\date{}|}.

Next are the dedications and acknowledgements:
\begin{quote}\tt\singlespace\begin{verbatim}
\begin{dedication}
To my pet rock, Skippy.
\end{dedication}

\begin{acknowledgments}
I thank the many people who have done lots of nice things for me.
\end{acknowledgments}
\end{verbatim}\end{quote}

You must tell \LaTeX{} to generate a table of contents, a list of tables and a list of
figures:
\begin{quote}\tt\singlespace\begin{verbatim}
\tableofcontents
\listoftables
\listoffigures
\end{verbatim}\end{quote}

If you wish to have a nomenclature, list of symbols or glossary it can go here.
\begin{quote}\tt\singlespace\begin{verbatim}
\begin{nomenclature}
%\begin{listofsymbols}
%\begin{glossary}
\begin{tabular}{ll}
$C_1$ & Constant 1\\
\ldots
\end{tabular}
%\end{glossary}
%\end{listofsymbols}
\end{nomenclature}
\end{verbatim}\end{quote}

If your abstract will be microfilmed by Bell and Howell (formerly UMI), then you
will need to generate an abstract of less than 350 words.  This abstract can be created
using the {\tt umiabstract} environment.  This environment requires that you define your
advisor and your advisor's title using {\tt \verb|\advisorname{}|} and
{\tt \verb|\advisortitle{}|}.
\begin{quote}\tt\singlespace\begin{verbatim}
\advisorname{Bucky J. Badger}
\advisortitle{Assistant Professor}
% ABSTRACT
\begin{umiabstract}
\noindent       % Don't indent first paragraph.
This explains the basics for using \LaTeX\ to typeset a
dissertation, thesis or project report for the University of
Wisconsin-Madison.

...

\end{umiabstract}
\end{verbatim}\end{quote}
This will place your name, title and required text at the top of the page and follow the
abstract text with your advisor's name at the bottom for your advisor's signature.  This
page is not numbered and would be submitted separately.

If you will have an abstract as part of your document, then the {\tt abstract} environment
should be used.
\begin{quote}\tt\singlespace\begin{verbatim}
\begin{abstract}
\noindent       % Don't indent first paragraph.
This explains the basics for using \LaTeX\ to typeset a
dissertation, thesis or project report for the University of
Wisconsin-Madison.

...

\end{abstract}
\end{verbatim}\end{quote}
This will generate a page number and it will be included in the Table
of Contents.  

If you will have both the UMI and regular abstracts like this document, then
you will probably want to write the abstract once and save it in a seperate
file such as {\tt abstract.tex}.  Then, you can use the same abstract for
both purposes.

\begin{quote}\begin{verbatim}
\begin{umiabstract}
  \input{abstract}
\end{umiabstract}

\begin{abstract}
  \input{abstract}
\end{abstract}
\end{verbatim}\end{quote}

Finally, the page numbers must be changed to arabic numbers to conclude the preliminary
portion of the document.
\begin{quote}\tt\singlespace\begin{verbatim}
\clearpage\pagenumbering{arabic}
\end{verbatim}\end{quote}

\section{The Body}
At the beginning of {\tt intro.tex} there is the following command:
\begin{quote}\tt\singlespace\begin{verbatim}
\chapter{Introducing the {\tt withesis} \LaTeX{} Style Guide}
\end{verbatim}\end{quote}
Following that is the text of the chapter.  The body of your thesis is separated by
sectioning commands like {\tt \verb|\chapter{}|}.  For more information on the sectioning
commands, see Section~\ref{ess:sectioning}.

Remember the basic rule of outlining you learned in grammar school:
\begin{quote}
You cannot have an `A' if you do not have a `B'
\end{quote}
Take care to have at least two {\tt \verb|\section|}s if you use the command; have
two {\tt \verb|\subsection|}s, {\em etc}.



\section{Additional Theorem Like Environments}
The {\tt withesis} style adds numerous additional theorem like environments.  These
environments were included to allow compatibility with the University of Wisconsin's
Math Department's style file.  These environments are
{\tt theorem}, {\tt assertion}, {\tt claim}, {\tt conjecture}, {\tt corollary},
{\tt definition}, {\tt example}, {\tt figger}, {\tt lemma}, {\tt prop} and {\tt remark}.

As an example, consider the following.
\begin{lemma}
Assuming that $\partial\Omega_2 = \emptyset$ and that $h(t) = 1$, we
have $$
\begin{array}{lr}
\Delta u = f, &  x\in\Omega ,\\[2pt]
u =  g_1, &  x\in\partial\Omega .
\end{array}
$$
\end{lemma}
which was produced with the following:
\begin{quote}\tt\singlespace\begin{verbatim}
\begin{lemma}
Assuming that $\partial\Omega_2 = \emptyset$ and that $h(t) = 1$, we
have $$
\begin{array}{lr}
\Delta u = f, &  x\in\Omega ,\\[2pt]
 u =  g_1, &  x\in\partial\Omega .
\end{array}
$$
\end{lemma}
\end{verbatim}\end{quote}

\section{Bibliography or References}
As a final note, the default title for the references chapter is ``LIST OF REFERENCES.''
Since some people may prefer ``BIBLIOGRAPHY'', the command
\break{\tt \verb|\altbibtitle|}
has been added to change the chapter title.

\section{Appendices}
There are two commands which are available to suppress the writing of the auxiliary information
(to the {\tt .lot} and {\tt .lof} files).  They are:
\begin{quote}\tt\singlespace\begin{verbatim}
\noappendixtables                % Don't have appendix tables
\noappendixfigures               % Don't have appendix figures
\end{verbatim}\end{quote}
These commands should be in the preamble.  See Section~\ref{usage:noapp}.

There are two environments for doing the appendix chapter: {\tt appendix} and
\break {\tt appendices}.  If you have only one chapter in the appendix, use the {\tt appendix}
environment.  If you have more than one chapter, like this manual, use the
{\tt appendices} environment.
\begin{quote}\tt\singlespace\footnotesize\begin{verbatim}
\begin{appendices}  % Start of the Appendix Chapters.  If there is only
                    % one Appendix Chapter, then use \begin{appendix}
\include{code}      % Including computer code listings
\include{bibref}    % a BibTeX reference
\include{math}      % Complex Equations from the UW Math Department

\end{appendices}    % End of the Appendix Chapters. ibid on \end{appendix}
\end{verbatim}\end{quote}
The difference between these two environments is the way that the chapter header is
created and how this is listed in the table of contents.
